%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=cyan,
  urlcolor=[rgb]{0,0,.4}
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textit{\normalsize{#1}}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & #4 \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\educationSubheading}[6]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2\vspace{1pt} \\
      {\normalsize#3} & #4\vspace{1pt} \\
      {\normalsize#5}\vspace{1pt} \\
      {\normalsize#6}\vspace{2pt} \\
      \ifx&#6&\vspace{-30pt}\fi  % super hacky and not correct spacing, but whatever
      
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubItem}[3]{
  \setlength{\itemsep}{1pt}
  \item\normalsize{
    \textbf{{#1}}{: \small{#2 \vspace{1pt}}} \\
    {\small{#3}\vspace{1pt}}
  }
}

\newcommand{\topHeadingItem}[2]{
  \setlength{\itemsep}{1pt}
  \item\normalsize{
    \textbf{\small{#1}}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\topHeadingListStart}{\begin{itemize}[label={}, leftmargin=0.05in, itemsep=0pt]}
\newcommand{\topHeadingListEnd}{\end{itemize}}


\renewcommand{\labelitemii}{$\circ$}

% adjust indentation of bullet points
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={}, leftmargin=0.05in]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={}, leftmargin=0.05in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\redstar}{\textcolor{red}{*}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  & \href{mailto:alexloftus2004@gmail.com}{\large{\faEnvelopeSquare} alexloftus2004@gmail.com}  \\ 
  % & \href{mailto:alexloftus2004@gmail.com}{\large{\faEnvelopeSquare} alexloftus2004@gmail.com} \\
  % & \href{https://github.com/loftusa}{\large{\faGithub} loftusa} \\
  \textbf{{\LARGE Alexander Loftus}} & \href{https://www.linkedin.com/in/alex-loftus/}{\large{\faLinkedinSquare} alex-loftus} \href{https://github.com/loftusa}{\large{\faGithub} loftusa} \href{https://alex-loftus.com}{\large{\faGlobe} alex-loftus.com} \\
\end{tabular*}

%-----------Summary of Qualifications-----------------
% \section{\centering Summary of Qualifications}
\noindent\color{black}\rule{\linewidth}{0.4pt}  % make a black horizontal line
I am a strong communicator and leader with deep technical expertise. I strive to help humans understand, evaluate, and control AI in more meaningful, powerful, and trustworthy ways. In the past, I have worked on representation learning, scalable systems, volumetric segmentation, and network statistics.

\vspace{4pt}
Some highlights:
\vspace{-2pt}
\topHeadingListStart
    \topHeadingItem{1st place ranking, \$100,000 Machine Learning competition}{\href{https://www.scientificamerican.com/article/inside-the-ai-competition-that-decoded-an-ancient-scroll-and-changed/}{Work featured on cover of Scientific American}. Competed against 1249 teams. Vesuvius scroll ink detection.}\vspace{-2pt}
    \topHeadingItem{Textbook author}{Publishing contract with Cambridge University Press.}\vspace{-2pt}
    \topHeadingItem{Teaching and Leadership}{Assistant director managing 10 team members; led a team of three to develop an object detection augmentation algorithm; led a team of five to contribute to a brain network estimation pipeline.}\vspace{-2pt}
    \topHeadingItem{Publications in top conferences}{Best poster award at NeurIPS 2023 LatinX workshop, first author work in ICLR 2024.}\vspace{-14pt} 
    \topHeadingItem{Open-source contributions}{Primary contributor to microsoft network statistics package graspologic.}
\topHeadingListEnd
    
    %--------PROGRAMMING SKILLS------------
%-----------TEXTBOOK-----------------
\section{Textbook}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://alex-loftus.com/files/textbook.pdf}{Hands-on Network Machine Learning}}{\textit{Eric Bridgeford, \textbf{Alexander R. Loftus}, Joshua Vogelstein.} Cambridge University Press, in copy-editing phase. To be printed November 2025.}{Spectral representation theory on networks. 530 pages, 147 figures.}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    % creyon
    \resumeSubheading
    {Data Scientist}{San Diego, CA}
    {Creyon Bio}{2022-2024}
    \resumeItemListStart
        \resumeItem{ESP Embeddings}{Developed contrastive feature representation learning approach for electrostatic potential data. Helped classify toxic drugs to save on drug testing costs.}
        \resumeItem{Neuron Toxicity Detection}{Built deconvolution and segmentation pipeline to detect toxicity in neurons. Resulted in a new drug discovery pipeline.}
      \resumeItemListEnd
  
  % IAI
    \resumeSubheading
    {Machine Learning Research Engineer}{Rockville, MD}
    {Blue Halo}{2021-2022}
    \resumeItemListStart
        \resumeItem{Conditional Image Generation with Generative Adversarial Networks}{Synthetic data augmentation. Led the switch to diffusion-based methods over GANs.}
        \resumeItem{Detecting Objects with Enhanced Yolo and Knowledge Graphs}{Used knowledge graphs to enhance object detection on videos.}
        \resumeItem{Geometric Multi-Resolution Analysis}{Infrastructure for a hierarchical clustering method.}
      \resumeItemListEnd
     % JHU
    \resumeSubheading
    {Artificial Intelligence Research Engineer}{Baltimore, MD}
    {Johns Hopkins University | Dr. Joshua Vogelstein}{2018-2021}
    \resumeItemListStart
    \resumeItem{\href{https://microsoft.github.io/graspologic/latest/}{Graspologic}}{Built dimensionality reduction models on networks.}
    \resumeItem{\href{https://neurodata.io/m2g/}{ndmg}}{Diffusion MRI to graphs pipeline. Kubernetes-orchestrated AWS cloud-computing integration with travis-based CI/CD infrastructure. Eliminated 1000 lines of code and halved computation time.}
    \resumeItemListEnd
    
    % ID TECH
    \resumeSubheading
    {Assistant Director}{Seattle, WA}
    {iD Tech Camps | University of Washington}{2014-2018 summers}
    \resumeItemListStart
    \resumeItem{Leader and Manager}{Administrator for a STEM education camp which taught C++, Python, Java, game design, and robotics at the University of Washington. Managed 8-12 instructors with 80-120 students per week.}
    \resumeItemListEnd

    % WWU
    % \resumeSubheading
    % {Research Assistant}{Bellingham, WA}
    % {Western Washington University}{2015-2018}
    % \resumeItemListStart
    % \resumeItem{Associative learning in C. elegans}{Python automation pipeline cut 5 days of work down to minutes. Resulted in research presented at the Society for Neuroscience, 2017.}
    % \resumeItemListEnd
    
\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \educationSubheading
      {Northeastern University}{Boston, MA}
      {\textit{PhD} Computer Science}{2024-}
      {\textit{Advisor}: \href{https://scholar.google.com/citations?user=CYI6cKgAAAAJ&hl=en&oi=ao}{Dr. David Bau}}
      {} \newline
      
      Interpretability, evaluations, and training dynamics in Code LLMs.
	    
    \educationSubheading
      {Johns Hopkins University}{Baltimore, MD}
      {\textit{MSE} Biomedical Engineering: Machine Learning \& Data Science Focus}{2020-2022}
      {\textit{Advisor}: \href{https://scholar.google.com/citations?user=DWPfdT4AAAAJ&hl=en&oi=ao}{Dr. Joshua Vogelstein}}
      {\textit{Thesis}: \href{https://alex-loftus.com/files/submitted_thesis.pdf}{Hands-On Network Machine Learning}}
      
      dean's list, highest honors, GPA 4.0/4.0.
	    
    \educationSubheading
      {Western Washington University}{Bellingham, WA}
      {\textit{BS} Behavioral Neuroscience | \textit{Minors}: Chemistry, Philosophy}{2014-2018}
      {\textit{Founder \& President}, Computational Neuroscience Club} 
      {\textit{Vice President}, Neuroscience Club}
      
      Built computational neuroscience club from scratch, taught weekly seminars.
     
  \resumeSubHeadingListEnd





%-----------------PUBLICATIONS-------------------


\section{Publications}

\small{\textcolor{red}{*} indicates equal contribution.}

\resumeSubHeadingListStart

\resumeSubItem{\href{https://openreview.net/forum?id=MxbEiFRf39}{NNsight and NDIF: Democratizing Access to Open-Weight Foundation Model Internals}}{\textit{\textbf{A.R. Loftus}\redstar, J.Fiotto-Kaufman\redstar, et al.} ICLR 2025.}{Infrastructure project to easily explore and manipulate foundation model internals with no engineering overhead.}

\resumeSubItem{\href{https://arxiv.org/abs/2311.06454}{A Saliency-based Clustering Framework for Identifying Aberrant Predictions}}{\textit{A. Tersol Montserrat, \textbf{A.R. Loftus}, Y. Daihes.} Paper, NeurIPS LatinX AI Workshop, 2023. \textbf{Won best poster.}}{Use embeddings of saliency map crops to identify predictions caused by spurious features.}

\resumeSubItem{\href{https://www.biorxiv.org/content/10.1101/2021.11.01.466686v2}{A low-resource reliable pipeline to democratize multi-modal connectome estimation and analysis}}{\textit{J. Chung, R. Lawrence, \textbf{A.R. Loftus}, et al}. Paper, in review at Nature Methods, 2024}{Turn diffusion MRI scans into adjacency matrices. \href{https://github.com/neurodata/m2g}{Code} on github.}

\resumeSubItem{Role of CAMKII in Associative Conditioning and GLR-1 Expression in C. Elegans}{\textit{M. Pribic, \textbf{A.R. Loftus}, et al}. Poster, Society for Neuroscience, 2017.} {Removing a protein involved in learning blocks associative conditioning in worms.}

\resumeSubHeadingListEnd

\section{Talks}

\resumeSubHeadingListStart

\resumeSubItem{\href{https://youtu.be/q9mC3T2aBL8}{State of the Art in Knowledge Editing}}{\textit{\textbf{A.R. Loftus}}, 2023}{Current techniques in knowledge localization and editing in LLMs and diffusion models.}

\resumeSubItem{\href{https://www.youtube.com/watch?v=IWySc8s00P0}{1st Place Solution - Vesuvius Ink Competition}}{\textit{R. Chesler, \textbf{A.R. Loftus}, A. Tersol Montserrat, T. Kyi}, 2023}{Presenting on our winning solution to a \$100,000 Kaggle competition, part of the \$1,000,000 Vesuvius competition.}

\resumeSubItem{\href{https://www.youtube.com/watch?v=V_hcmfdJzF8}{ICML Conference Highlights}}{\textit{\textbf{A.R. Loftus}}, 2023} {Machine learning techniques in drug discovery and medicine at ICML 2023.}

\resumeSubItem{\href{https://lu.ma/aisd1}{Working with LLMs}}{\textit{\textbf{A.R. Loftus}}, 2023.} {Introduction to LLM engineering. Talk given to 100 people at the AI/ML San Diego meetup.}

\resumeSubItem{\href{https://www.youtube.com/playlist?list=PLlP-93ntHnnu-ETNlIfelO9C6T8VrADAh}{Linear Algebra, from Dot Products to Neural Networks}}{\textit{\textbf{A.R. Loftus}}, 2023.} {Created a YouTube tutorial series on the fundamentals of linear algebra for machine learning.}

\resumeSubItem{Effects of an unc-43 (CaMKII) Gene Deletion on Short-Term Memory for Associative Conditioning in C. elegans}{\textit{\textbf{A.R. Loftus}}, Psychfest 2017.} {Mechanistic understanding of worm neural circuitry.}

\resumeSubHeadingListEnd

%-----------------GRANTS-------------------
\section{Fellowships \& Awards}
\topHeadingListStart

    \resumeSubheading
    {First Place Winner}{}
    {\href{https://www.kaggle.com/competitions/vesuvius-challenge-ink-detection/overview}{Kaggle Vesuvius Competition, \$100,000.}}{2023}
    
    \resumeSubheading
    {Khoury Distinguished Fellowship}{}
    {Northeastern University PhD fellowship.}{2024}
    
    \resumeSubheading
    {Best Poster Award}{}
    {NeurIPS 2023 LatinX AI Workshop.}{2023}

    \resumeSubheading
    {MIT EECS GAAP}{2023}
    {MIT mentorship program.}

    \resumeSubheading
    {Harvard AI Safety Technical Fellowship}{2025}
    {Harvard fellowship.}

    \resumeSubheading
    {AWS Research Grant}{}
    {\$10,000 grant for computational research on cloud services.}{2019}

\topHeadingListEnd



\section{Service \& Advisory}
\resumeSubHeadingListStart
    \resumeSubheading
    {Consultant}{Krnel.ai}
    {Advisory role for cybersecurity-based interpretability startup.}{Spring 2025}
    
    \resumeSubheading
    {Organizer}{NEMI}
    {Organizing the 200-person New England Mechanistic Interpretability conference. Obtained \$17,000 grant.}{Summer 2025}
    
\resumeSubHeadingListEnd
%-----------------GRANTS-------------------
\section{Teaching}
\resumeSubHeadingListStart

    \resumeSubheading
    {Head Teaching Assistant}{Johns Hopkins University}
    {Foundations of Computational Biology and Bioinformatics, \textit{EN.BME.410/634}}{Spring 2021}
    
    \resumeSubheading
    {Teaching Assistant}{Johns Hopkins University}
    {\href{https://neurodatadesign.io/}{NeuroData Design II}, \textit{EN.BME.438/638}}{Spring 2020}
    
    \resumeSubheading
    {Teaching Assistant}{Johns Hopkins University}
    {\href{https://neurodatadesign.io/}{NeuroData Design I}, \textit{EN.BME.437/637}}{Fall 2019}

    \resumeSubheading
    {Teaching Assistant}{Western Washington University}
    {Introduction to Behavioral Neuroscience, \textit{PSY.220}}{Winter 2017}
    
    \resumeSubheading
    {Curriculum Designer}{iD Tech Camps}
    {Built curriculum used across 50 locations in the United States by tens of thousands of students.}{Spring 2017}
    
    \resumeSubheading
    {Instructor}{iD Tech Camps}
    {Taught programming and game design to high school students.}{2014-2018 summers}


\resumeSubHeadingListEnd

\section{Skills Summary}
    \resumeSubHeadingListStart
        \resumeSubItem{Languages}{Python, R, Rust, Bash, CSS, Mojo, English, Broken Spanish}{}
        \resumeSubItem{Tools \& Frameworks}{pytorch, pytorch-lightning, tensorflow, jax, numpy, scipy, pandas, polars, sklearn, seaborn, matplotlib, docker, AWS, google cloud (GCP), photoshop, SQL, weights \& biases, mlflow, kubernetes, linux}{}
        \resumeSubItem{Areas of Expertise}{Linear algebra, probability \& statistics, deep learning, information theory, transformers, diffusion models, convolutional autoencoders, GPUs and CUDA, public speaking, leadership \& management, teaching, natural language processing, computer vision}{}
    \resumeSubHeadingListEnd

\section{Fun}
    \resumeSubHeadingListStart
        \resumeSubItem{Gaming}{Starcraft 2 grandmaster in high school, competed and won in Seattle-area tournaments.}{}
        \resumeSubItem{Music}{Fingerstyle guitarist. Played at open mic nights.}{}
        \resumeSubItem{Dancing}{Partner dance instructor and competition winner. Fusion, West Coast Swing, Zouk, Salsa, Bachatta.}{}
    \resumeSubHeadingListEnd
    
%-----------PROJECTS-----------------
% \section{Academic, Personal, \& Open-Source Projects}
% \resumeSubHeadingListStart
% \resumeSubItem{\href{https://github.com/neurodata/graphutils}{graphutils}}{Utility functions and statistics library for use on networks stored in AWS S3 buckets.}
% \resumeSubItem{\href{https://github.com/loftusa/genetic-correlates-adhd}{Genetic Correlates of ADHD}}{Using a dataset of 50,000 ADHD genomes, including my own, to try to reduce noise in finding genes correlated with ADHD. Summary poster \href{https://i.ibb.co/cx5PVmB/Slide1.png}{here.}}
% \resumeSubItem{\href{https://github.com/loftusa/mri-code-challenge/blob/master/Main-analysis.ipynb}{MRI Session Classifier}}{Exploratory data analysis on basic MRI data.}
% \resumeSubItem{\href{https://github.com/loftusa/Dota-Stats}{Dota 2 Stats}}{Data analysis from statistics I generated while playing the video game dota 2, exploring the strengths and weaknesses of various characters with respect to my own playstyle.}
% \resumeSubItem{\href{https://github.com/loftusa/General-Projects-And-Scripts}{Early Projects}}{Scripts and mini-projects from early years. Includes a web scraper for chemical compounds, estimations of basketball free-throw probabilities, grade trends, and code implementations of every chapter of two textbooks (linear algebra and data science)}


% \resumeSubHeadingListEnd

% \section{Self-learning / Informal Education}
% \resumeSubHeadingListStart
% \resumeSubItem{\href{https://www.codecademy.com/learn/learn-python-3}{Learn Python: Codecademy}} {Finished full course.}

% \resumeSubItem{\href{https://automatetheboringstuff.com/}{Automate the Boring Stuff with Python}} {Finished full course.}

% \resumeSubItem{\href{https://www.amazon.com/Introducing-Python-Modern-Computing-Packages/dp/1449359361}{Introducing Python}} {Finished book cover-to-cover.}

% \resumeSubItem{\href{https://jakevdp.github.io/PythonDataScienceHandbook/}{Python Data Science Handbook}}{ Finished cover-to-cover.}

% \resumeSubItem{\href{https://www.khanacademy.org/}{Khan Academy}} {Finished multivariate calculus series.}

% \resumeSubItem{\href{https://linear.axler.net/}{Linear Algebra Done Right - Sheldon Axler}} {Finished entire textbook and 1/4 of the exercises.}

% \resumeSubItem{\href{https://www.amazon.com/Mathematics-Discrete-Introduction-Edward-Scheinerman/dp/0840049420}{Mathematics: A Discrete Introduction}} {Finished cover-to-cover and 1/2 of the exercises.}

% \resumeSubItem{\href{https://ocw.mit.edu/courses/18-065-matrix-methods-in-data-analysis-signal-processing-and-machine-learning-spring-2018/}{MIT OpenCourseware: Matrix Methods for Machine Learning}} {Finished entire course}

% \resumeSubItem{\href{https://ocw.mit.edu/courses/res-18-010-a-2020-vision-of-linear-algebra-spring-2020/}{MIT OpenCourseware: A 2020 Vision of Linear Algebra}} {Finished entire course}

% \resumeSubItem{\href{https://github.com/ageron/handson-ml3}{Hands-On Machine Learning with Scikit-Learn, Keras and Tensorflow}} {Finished textbook}

% \resumeSubItem{\href{https://course.fast.ai/}{Practical deep learning for coders}} {Finished full course}

% \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
